Mapping out the punishment strategy space

### 2023-11-24 report.Rmd
finished manuscript first draft

We assume here that people are following a particular strategy exactly and are not comitting any errors or mistakes. However, it is possible that some participants intended to follow a particular strategy, but made a mistake on a particular decision. We repeat the counts and proportions in the table above, but include behavioural patterns that have one mistake from the exact strategy (note that the proportions will no longer sum to 1).

```{r strategyCountsMistake1}
kable(tar_read(tableStrategyCounts_Mistake1), booktabs = TRUE)
```

And including behavioural patterns that have one or two mistakes.

```{r strategyCountsMistake2}
kable(tar_read(tableStrategyCounts_Mistake2), booktabs = TRUE)
```

And finally, including behavioural patterns that have one, two, or three mistakes.

```{r strategyCountsMistake3}
kable(tar_read(tableStrategyCounts_Mistake3), booktabs = TRUE)
```

@@

```{r echo=F}
tar_read(plotDemsNoTPP)
```

@@

```{r echo=F}
tar_read(plotSlidersNoTPP)
```

@@

```{r echo=F}
tar_read(plotPersNoTPP)
```

@@

```{r echo=F}
tar_read(plotPolRelNoTPP)
```

>>>>

@@

```{r echo=F}
tar_read(plotAllDems2)
```

@@

```{r echo=F}
tar_read(plotAllSliders2)
```

@@

```{r echo=F}
tar_read(plotAllPers2)
```

@@

```{r echo=F}
tar_read(plotAllPolRel2)
```
